
1)we we want to keep debugger (that mean in which line inside function or outside the function)
2)how to track javascript code by using html elemt (to open code in source tab) by uing event listiner.
3)two types of files are present full code and minified (how can we get full code insteaded of minified).
4)how can we use page option in sourece tab.
5)when we use console.
6)buttons of debugger 1)pass script execution. (to stop the execution of output of script) /and resume the execution of script
                      2)stepover function call.
                      3)stepinto next function call.
                      4)step outof current function
                      5)step
                      6)de activate breakpoints.
                      7)pause on exceptions
7)right side menu option-->1)watch (i done video)
                        -->2)breakpoints (check the screen shot (it act like css check and un check)
                        -->3)call stack
                        -->4)scope (i done video)
                        --5)xhr/fetch break points
                        -->6)dom breakpoints
                        -->7) event listiner breakpoints
                        -->8)csp violation breakpoints

8)edit the code in source tab and check the output(some times editing is possible some times not possible find the reason)

-----------------------------
1)two types of function call present a)in html page(java script) b)in js page(jquery) (based on whre we do function call the event break point give code).
2)learn debugger option by uing different  type of funcction syntax-->1)functions /function call
                                                                   -->object calling 

functions
function call
how ca we track wethere the function calling pending or function called
---------------
1)function call in bookmars

.

